### 2020-01-08 report/02-methods.Rmd
Simplify SEM (only evt) + function to rm sp from community_analysis

```{r}
pca_clim_phy_press <- map(
  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  function(.data) dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE))

names(pca_clim_phy_press) <- c("med_evt", "cv_evt", "med_press", "cv_press")
```

@@

```{r}
pca_rotated <- map2( 
  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  c("Med evt", "Cv evt", "Med press", "Cv press"),
  function(.data, title) {
    .data %<>% na.omit
    pca <- dudi.pca(as.data.frame(.data), scannf = FALSE, nf = 2, center = TRUE, scale = TRUE)
    pca_rotated <- psych::principal(.data, rotate="varimax", nfactors=2,
      scores=TRUE)

    return(list(normal = pca, rotated = pca_rotated))

  })
names(pca_rotated) <- c("med_evt", "cv_evt", "med_press", "cv_press")

test <- vector(mode = "list", length = 4)
for (i in seq_along(names(pca_rotated))) {

  s.corcircle(
    pca_rotated[[i]]$rotated$loadings[1:nrow(pca_rotated[[i]]$rotated$loadings),], xax = 1,
    yax = 2)
  rotated_plot <- recordPlot()

   pca_plot <- fviz_pca_var(pca_rotated[[i]]$normal,
      axes = c(1, 2),
      col.var = "contrib", # Color by contributions to the PC
      gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
      repel = TRUE # Avoid text overlapping
    )

  test[[i]] <- plot_grid(rotated_plot, pca_plot)
  rm(rotated_plot)

}
plot_grid(plotlist=test)
mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
```

@@

>>>>

```{r}
pca_clim_phy_press <- map(
  list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  function(.data) dudi.pca(as.data.frame(na.omit(.data)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE))
names(pca_clim_phy_press) <- c("med_evt", "cv_evt", "med_press", "cv_press")
```

@@

```{r, fig.show = "hide"}
pca_rotated <- compute_rotated_pca(
  data_list = list(hab_evt_mean, hab_evt_cv, hab_press_mean, hab_press_cv),
  titles = c("med_evt", "cv_evt", "med_press", "cv_press")
)

test <- plot_rotated_pca(pca_rotated)

mysave(pca_rotated, dir = mypath("report"), overwrite = TRUE)
```

```{r pca_rotated_plot}
plot_grid(plotlist=test)
```

#### Rotate PCA axis 2

```{r pca-data, fig.show = "hide"}
evt_var_mean_ok <-  c(evt_var_mean, "DBO_med")
evt_var_cv_ok <-  c(evt_var_cv, "DBO_cv")
pca_pressure <- habitat_pressure[, names(habitat_pressure) %in% c(evt_var_mean_ok, evt_var_cv_ok, "station")] %>% 
  na.omit

pca_list <- map(list(evt_var_mean_ok, evt_var_cv_ok), function (.var) {
  pca_pressure[, names(pca_pressure) %in% .var]
})
names(pca_list) <- c("evt_med", "evt_cv")

pca_rotated <- compute_rotated_pca(
  data_list = pca_list,
  titles = names(pca_list)  
)

pca_rotated_plot <- plot_rotated_pca(pca_rotated = pca_rotated)
```

```{r pca_env_ok}
plot_grid(plotlist = pca_rotated_plot, ncol = 1)
```

@@

#### Species occurence

```{r}
myload(community_analysis, dir = data_common)

com <- community_analysis %>%
  dplyr::select(opcod, species, biomass) %>%
  dplyr::left_join(op_analysis[, c("opcod", "station")], by = "opcod") %>%
  dplyr::filter(!is.na(station)) %>%
  dplyr::group_by(station) %>%
  tidyr::nest() %>%
  mutate(data = map(data, function (.data) {
      .data %<>%
	tidyr::spread(species, biomass) %>%
	dplyr::select(-opcod) %>%
	dplyr::mutate_all(list(~ ifelse(is.na(.), 0, .))) %>%
	dplyr::summarise_all(list(~ sum(. != 0) / n()))
      return(.data)
      }
    )
  )
occurence_sp_st <- com %>%
  unnest() 
%>%
  dplyr::mutate_if(is.double, list(~ ifelse(is.na(.), 0, .)))

med_occ <- occurence_sp_st %>%
  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
  gather(sp, med_occ, everything())

med_occ %>%
  ggplot(aes(x = med_occ)) +
  geom_histogram()

```{r}
sp_per <- med_occ[med_occ$med_occ < .30,]$sp

threshold_occ <- c(.10, .30, .50, .80)
com_wo_per  <- map(threshold_occ, ~ rm_sp_from_com(com = community_analysis, sp_to_rm =
    med_occ[med_occ$med_occ < .x,]$sp))
names(com_wo_per) <- threshold_occ

com_data <- list(total = community_analysis)
com_data <- c(com_data, com_wo_per)

res_sync_per <- map2(com_data, names(com_data), function (.data, .names) {

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = .data)
  sync$type <- .names 
  sync$biomass_stab <- 1 / sync$cv_com
  return(sync)

})

test <- do.call(rbind, res_sync_per)

test %>%
  ggplot(aes(x = richness_med, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type))

### 2020-01-08 report/05-stability.Rmd
Simplify SEM (only evt) + function to rm sp from community_analysis

```{r}

@@

```{r}
library(nlme)
library(piecewiseSEM)

@@

```{r}
ggpiecewisesem(sem)
```

- Main results:
  - Richness destabilizes communities 
  - Turnover destabilizes communities, latter increased by enrichment
  - Trophic level decreased CV but increase species synchrony!
  - Connectance!

```{r sensitivity, eval = FALSE}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))

sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    dest_dir = mypath("data", "species"))
)

@@

```{r, fig.cap = "Biomass"}
prod_sem <- psem(
  lme(temperature_med ~ alt, random = ~ 1 | basin, data = lav_data),
  lme(log_rich ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(piel ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(c_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(t_lvl ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(beta_bin_c ~ alt + width + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data),
  lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + DBO_med + temperature_med, random = ~ 1 | basin, data = lav_data)
)
sumup_prod <- summary(prod_sem, .progressBar = F)
sumup_prod$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r}
ggpiecewisesem(sumup_prod)
```

```{r colin_prod}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + temperature_med + DBO_med, random = ~ 1 | basin, data = lav_data))
```

>>>>

@@

```{r, fig.dim = c(10, 7), echo = FALSE, fig.cap = "SEM for stability"}
library(nlme)
library(piecewiseSEM)

@@

ggpiecewisesem(sem)
```

- Main results:
  - Richness destabilizes communities 
  - 
  - Trophic level decreased CV but increase species synchrony!
  - Connectance!

```{r sensitivity, fig.dim = c(14, 7), fig.cap = "Sensivity analysis with different dataset"}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    dest_dir = mypath("data", "species"))
)

@@

```{r, fig.cap = "Coefficients of the SEM of biomass"}

prod_sem <- compute_prod_sem(.data = sem_data)

prod_sem$coefficients %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "400px")
```

```{r}
ggpiecewisesem(prod_sem)
```

```{r colin_prod, fig.cap = "Colinearity check for total biomass"}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + evt_med1 + evt_med2 + evt_cv1 + evt_cv2, random = ~ 1 | basin, data = sem_data)) %>%
  enframe %>%
  kable
```
